External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
add

\subsection{Real Image Denoising}

In the last decade, researchers proposed many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. The method of ``Noise Clinic" \cite{noiseclinic,ncwebsite} and the software of Neat Image \cite{neatimage} are developed specifically for real noisy image denoising. ``Noise Clinic" \cite{noiseclinic,ncwebsite} generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is often time consuming.

@@

In this section, we formulate the framework of external patch group (PG) prior guided internal prior learning. We first introduce the external PG prior leaning on natural clean RGB images. Then we propose to employ the learned external PG prior to guide the internal prior (subspace selection and dictionary learning (DL)) learning of given degraded (such as noisy) images. Under the weighted sparse coding framework, the internal prior learning process has alternative closed-form solutions in term of updating sparse coefficients and orthogonal dictionary. Finally, we discuss in details how external prior learned from natural clean images guide the internal prior learning of given degraded (noisy) images.

@@

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-3mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  \textbf{39.57}  & 667.36 & 43.77
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}

>>>>

\subsection{Real Noisy Image Denoising}

In the last decade, there are many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem. These methods can be applied to real noisy image denoising directly. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. The method of ``Noise Clinic" \cite{noiseclinic,ncwebsite} and the software of Neat Image \cite{neatimage} are developed specifically for real noisy image denoising. ``Noise Clinic" \cite{noiseclinic,ncwebsite} generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is often time consuming.

@@

In this section, we first describe the learning of external prior, and then describe in detail the guided internal prior learning. Finally, the denoising algorithm with the learned priors is presented.

@@

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-3mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  \textbf{39.57}  & 667.36 & 41.89
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}
